Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-05 paper.tex
Modified Section 4.1

We processed the the data so that data records with matching pairs of origin and destination (OD) station names are aggregated. To do so, several technical

 This is facilitaed with the open-source reconciliator \todo{one liner that describes how this works} situated at \url{https://github.com/irail/stations}.

To address this challenge, an open-source reconciliator (\url{https://github.com/irail/stations}) was employed to reduce spelling variations and correct errors.

Each data record now contains the station object of both origin and destination (OD), the user agent that made the query, as well as the time when the query was made.
As we were specifically interested in studying morning and evening rush hour travel that occur on weekdays, we filtered the dataset to exclude data records created outside the time range of \todo{PC: we will have to explain ourselves why we'd choose different hours than what we've found above} 06:00~hrs and 10:00~hrs as well as 17:00~hrs and 21:00~hrs on weekdays, and all data records created on weekend. Queries made by automated user agents like search engine bots and data harvesters were also excluded from the dataset to remove biases that may over represent connections between certain stations. Similarly, data records with unparsable origin or destination station names due to spelling mistakes or invalid character encoding were removed as well.

>>>>

The data is formatted in a manner where data records with matching pairs of origin and destination (OD) station names are aggregated. 
To arrive at this outcome several technical challenges must be addressed.
One distinctive challenge is the substantial amount of inconsistency in the manner where origin and destination (OD) station names are defined. 
Spelling mistakes as well as the use of unstandardized abbreviations in particular, reduce the quality and accuracy of aggregation.
To overcome this challenge, an open-source reconciliator (\url{https://github.com/irail/stations}) was employed to reduce spelling variations and correct identifiable errors.

As we were specifically interested in studying morning and evening rush hour travel that occur on weekdays, we filtered the dataset to exclude data records created outside the time range of \todo{PC: we will have to explain ourselves why we'd choose different hours than what we've found above} 06:00~hrs and 10:00~hrs as well as 17:00~hrs and 21:00~hrs on weekdays, and all data records created on weekend. Queries made by automated user agents like search engine bots and data harvesters were also excluded from the dataset to remove biases that may over represent connections between certain stations. Similarly, data records with unparsable origin or destination station names due to spelling mistakes or invalid character encoding were removed as well.
